---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/"
)
```

# bossr

<!-- badges: start --
[![CRAN Status](https://www.r-pkg.org/badges/version/pkgdown)](https://cran.r-project.org/package=pkgdown){.pkgdown-release}
[![R-CMD-check](https://github.com/r-lib/pkgdown/workflows/R-CMD-check/badge.svg)](https://github.com/r-lib/pkgdown/actions){.pkgdown-devel}
[![Codecov test coverage](https://codecov.io/gh/r-lib/pkgdown/branch/main/graph/badge.svg)](https://app.codecov.io/gh/r-lib/pkgdown?branch=main)
 badges: end -->

bossr consists of functions for automated segmentation of oligodendrocytes in 2D, 3D and 4D arrays. A companion data package 'bossrdata' is available to enable users to follow along the examples in the vignettes. See the vignettes for more information on how to install 'bossrdata'.

## Installation

```{r, eval = FALSE}
# Install released version from our drat repository
install.packages("bossr", repos='https://pennsive.github.io/drat')
```

or the install the development 

```{r, eval=FALSE}
devtools::install_github('pennsive/bossr')
```

You can also choose to install an example dataset to get started [TODO: add link] with using bossr.

```{r, eval = FALSE}
# Install the companion package
install.packages("bossrdata", repos='https://pennsive.github.io/drat')
```

