---
title: "Introduction to the bossr pipeline"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  cache = TRUE,
  cache.path = 'cache/',
  cache.lazy = TRUE,
  comment = "#>"
)
```

Install the companion package to follow along the vignette: `install.packages('bossrdata', repos = 'https://pennsive.github.io/drat', type='source')`. 


```{r setup}
library(bossr)
library(bossrdata)
data(oligo)
```

The `oligo` dataset in `bossrdata` consists of a small 4D array from a region-of-interest in cortex from an adult transgenic mouse expressing EGFP in the cytoplasm of oligodendrocytes (MOBP-EGFP). This same region was imaged at least weekly using two-photon imaging through a cranial window over the course of cuprizone-treatment and recovery. 

```{r oligo}
# Oligo is a 4D array
str(oligo)
```

The array functions in bossr are easily parallelizable and detect dimensionality of the input array. The first function in the pipeline, `bossr::betamix_img()`, produces a threshold for each slice of an array. 

```{r betamix.img}
n.cores = parallel::detectCores() # detect cores automatically (or can also be set manually)
thr <- bossr::betamix_img(oligo, n.cores = n.cores)
```

The resulting threshold can be applied with `bossr::threshold_img()`, which produces a mask.

```{r threshold}
mask <- bossr::threshold_img(oligo, thr, n.cores = n.cores)
```

Below, we visualize the results of the masking operation for `z=1` and `t=1`. To the left the original array; to the right the resulting mask.

```{r, echo=FALSE, fig.show="hold", out.width="50%"}
oro.nifti::slice(oligo)
oro.nifti::slice(mask)
```

After thresholding, `bossr::median_filtering()` is applied to reduce noise in the mask. 

```{r median_filtering}
mask_filtered <- bossr::median_filtering(mask)
```

```{r, echo=FALSE, fig.show="hold", out.width="50%"}
oro.nifti::slice(oligo)
oro.nifti::slice(mask_filtered)
```

And once the mask has been filtered, `bossr::connect_components()` will detect individual cells via a connected components algorithm. This operation will result in distinct labels being produced for each cell.

```{r connect_components}
labels <- bossr::connect_components(mask_filtered)
```

To produce a description of the location and size of each cell, we use `bossr::track_components()` followed by `bossr::post_process_df()` to perform imputation of cells across timepoints. These two functions output a `data.frame` and can be easily piped. 

```{r cell_df}
cell_df <- bossr::track_components(labels) |> 
  bossr::post_process_df()
head(cell_df)
```

A summary of how cell counts change over time can be produced with `bossr::annotate_df()` (see function reference for details on column meanings).

```{r annotate_df}
bossr::annotate_df(cell_df, t = 4)
```

Then, we can produce a 3D overlay that draws a box around each cells centroid with `bossr::make_overlay()`: we just need to pick a time point and specify the overlay dimensions. 

```{r}
my_overlay <- bossr::make_overlay(cell_df, dim(oligo), t = 1)
```

For `t = 1` the first cell in `cell_df` has a centroid at `z = 67`: to help us examine the correctness of this entry, we can use `bossr::plot_overlay()` which takes a 3D image, an overlay made by `bossr::make_overlay()` and chosen slice `z`. We 

```{r}
bossr::plot_overlay(oligo[,,,1], my_overlay, z = 67)
```

We see that the centroid is correctly specified for the upper cell. The bottom cell's centroid is at `z = 7` so it won't show up in this slice.

```{r}
bossr::plot_overlay(oligo[,,,1], my_overlay, z = 7)
```


